Notes and approaches to OCR

### 2020-09-03 outputs/documents/paper.Rmd
Include validation of Google API

```{r echo=FALSE}
library("reticulate")
```

@@

```{python}
import os
import sys
import requests
# If you are using a Jupyter notebook, uncomment the following line.
#%matplotlib inline
import matplotlib.pyplot as plt
from matplotlib.patches import Rectangle
from PIL import Image
from io import BytesIO
import matplotlib
import matplotlib.font_manager as font_manager
from os import path
import ast
```

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1.png)
**Figure 1**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2.png)
 **Figure 2**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3.png)   
 **Figure 3**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4.png)
 **Figure 4**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5.png)
 **Figure 5**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure6.png)
 **Figure 6**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure7.png)
 **Figure 7**

@@

@@

@@

>>>>

```{r echo=FALSE, include=FALSE, warning=FALSE}
library("reticulate")
```

@@

```{python eval=FALSE, include=TRUE}
import os
import sys
import requests
# If you are using a Jupyter notebook, uncomment the following line.
#%matplotlib inline
import matplotlib.pyplot as plt
from matplotlib.patches import Rectangle
from PIL import Image
from io import BytesIO
import matplotlib
from os import path
import ast
```

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure1_full.png)
**Figure 1**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure2_full.png)
 **Figure 2**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure3_full.png)   
 **Figure 3**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure4_full.png)
 **Figure 4**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure5_full.png)
 **Figure 5**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure6_full.png)
 **Figure 6**

@@

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure7_full.png)
 **Figure 7**

@@

## Google Vision OCR

Google Vision API can integrate vision detection features, including image labeling, face and landmark detection, optical character recognition (OCR), and tagging of explicit content. The text recognition process detects text in images and recognizes the text contained therein. Once detected, the recognizer then determines the actual text in each block and segments it into lines and words.

To evaluate this OCR option, we need the following python libraries.

```{python eval=FALSE, include=TRUE}
from os import path
from PIL import Image
from PIL import ImageFont
from PIL import ImageDraw
from PIL import ImageEnhance
import base64 #Convert an image into base64 form for API requests
import requests #API request - GET/POST
import json
import ast
```

Same as the Azure API, we need to create the headers and parameters necessary for calling the API. We also need the python library **requests** to make the API call. The method **post** is needed as the API uses the HTTP method POST.

The following example illustrates how to state the headers and parameter, but also create two functions. The first one, called encode_image converts an image into base64, an encoding process designed to carry data stored in binary formats across channels that only reliably support text content. It can embed image files or other binary assets inside textual assets. The second one makes an HTTP POST request that calls Google's Vision API.

```{python eval=FALSE, include=TRUE}
#Create the URL for the API call. The endpoint corresponds to the Azure's 
# endpoint of the account.
url = "https://vision.googleapis.com/v1/images:annotate"

querystring = {"key": google_vision_api_key }
headers = {'Content-Type': "application/json"}

def encode_image(image_path):
    with open(image_path, "rb") as image_file:
        return base64.b64encode(image_file.read())

def image_request(image_path):

    payload = '{\"requests\":[{\"image\":{\"content\":\"'+
    encode_image(image_path).decode('utf-8')+
    '"},\"features\":[{\"type\":\"TEXT_DETECTION\"}]}]}'

    response = requests.request("POST", url, data=payload, headers=headers, params=querystring)

    return ast.literal_eval(response.text)
```

This is an example of the response:

```{} 
{'responses': [{'textAnnotations': [{'locale': 'ja',
     'description': '-]\n一\n一本の傘を二人でさすこと。多く男女二人の場合に一あい-えん [哀婉](名) 哀れにやさしいこと。 こと。しん【愛郷心](名) 愛婚の精神。.............名)あいく\n-[製~Q)
     れ]()あ\nの。0子持鮎の願漬。\nあいきょうp®(愛郷](名)生まれ故郷を愛する\nに\nVド\nし
     いこと。叉、その程度。\n信的思想た打破すること。\n',
     'boundingPoly': {'vertices': [{'x': 26, 'y': 21},
       {'x': 1556, 'y': 21},
       {'x': 1556, 'y': 2748},
       {'x': 26, 'y': 2748}]}},
    {'description': '-',
     'boundingPoly': {'vertices': [{'x': 1227, 'y': 686},
       {'x': 1227, 'y': 677},
       {'x': 1262, 'y': 677},
       {'x': 1262, 'y': 686}]}},

       すること。\n'}}]}
           {'description': '誘',
     'boundingPoly': {'vertices': [{'x': 785, 'y': 880},
       {'x': 814, 'y': 880},
       {'x': 814, 'y': 914},
       {'x': 785, 'y': 914}]}},
    {'description': '(',
     'boundingPoly': {'vertices': [{'x': 775, 'y': 916},
       {'x': 814, 'y': 916},
       {'x': 814, 'y': 940},
       {'x': 775, 'y': 940}]}},
    ...],
```

From the previous example, we can observe that the response returns a list of nested dictionaries. The first nested dictionary called **textAnnotations** consists of a list of nested dictionaries. Each one of those has a description (character) and boundingPoly (boundaries of the characters).

### BoundingPoly

Each boundingPoly consist of vertices in which the symbol is located.

#### Region

Te first object in the nested dictionary contains all identified characters in the image as well as the boundaries that comprises the location of those characters. This object can resemble the idea of the region provided in the Azure's API.

Figure 8 shows the region identified by the API.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure8.png)
 **Figure 8**

#### The Character Boundaries

The remaining objects enclose the boundaries of the characters. As it is shown in figure 9, each boundingPoly node can include one or more characters.

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure9.png)
**Figure 9**

Once the bounding boxes are located, each character takes its corresponding place, as it is shown in figure 10. **Pending find a way to plot the text in vertical form to make it readable.**

![image](E:/Users/Usuario/Documents/GitHub_Website/website/japanese_dictionaries/outputs/documents/figure10.png)
**Figure 10**

### languageHints

Google Vision API offers the advantage of including in the request language hints. It consists of a list of languages the user knows in advance the image contains. For this study, we run two versions, one without hints and the other one with a list of two hints, such as Japanese and English, as the image contains some words in English.

Same as the Azure API, this is also easy to use after reading the documentation. It also offers several examples in different programming languages using the Google libraries for Python. It gives the possibility to include languages in advanced as hints, and identifies the orientation automatically. The response contains an object with all identified characters in the correct order.

Moreover, the API gives the opportunity to send the image in base64 format or using an internal (google storage) or external URL.

Not clear at the moment.....I need to solve how to plot grouped characters vertically.

### Future Work

.........

@@

# Appendix

@@

6: https://cloud.google.com/vision/docs/ocr
